---
title: "Lab3"
author: "YenTing Shen"
date: "1/29/2019"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```
#Lab 3

### Team Question:

The question that we will try to answer as a team is if smoking lowers a person's overall health. This question is importatnt because a lot of people worldwide smoke cigarettes, and it is very useful to know if they have a detrimental effect on one's health and well-being.

### Individual Plots

The following is a graph of height versus weight, with different colors differentiating between smokers and non smokers. I, Jason Giblin, created this plot. In this data set, height is measured in inches, and weight is measured in pounds. Non-smoker is defined as a person who has smoked less than 100 cigarettes in their life, and smoker is defined as someone who has smoked at least 100 cigarettes in their life. This plot shows that in general, as height increases, weight also increases, as expected. Another interesting bit about this graph is that it appears smokers and non-smokers don't differ by too much in height and weight. With the exception of the two tails of the graph, the best fit lines for smokers and non-smokers are nearly identical. Some adjustments I made to the basic plot was first of all, adding the smooth best fit curve. Additionally, I used colors to differentiate between 2 groups: smokers and non-smokers. I used this color pattern for both the scatter plot and smooth curve. I changed the key to the right of the graph to say "non-smoker" and "smoker." Lastly, I added labels for the title of the graph, and intuitive labels for each of the axes.

```{r}
ggplot(data=cdc, aes(x = height, y = weight, color=as.factor(smoke100)))+
  geom_point()+
  geom_smooth()+
  xlab('height (inches)')+
  ylab('weight (lbs)')+
  ggtitle('Height versus Weight for Smokers and Non-Smokers')+
  scale_color_discrete(name = 'Smoking Habits',
                       labels = c('non-smoker', 'smoker'))


```




The graph below was make by Emery Schattinger, it shows how smoking can cause your health to have problems by having a graph that compared the health of non smokers and the health of smokers. With the graph you can see that with the group of people who smoke, they tend to have more people with lower health quality and fewer people with better health. When I was going about making the graph, I first picked which variaables I wanted to use, then I desided to split the data up into smokers vs non smokers so it wouldn't be hard to compare the two. Then I thought it would be a good idea to change the colors for the different Health Qualities so you know exactly which two section to compare to. I like thiis graph because it was simple and strait to the point.

```{r}
ggplot(data = cdc) + 
  geom_bar(mapping = aes(x = smoke100, fill = genhlth)) +
  ggtitle("Health of Non Smokers vs. Smokers") +
  labs(y= "People", x = "Non Smokers                                              Smokers")+
  labs(fill ="Health Quality")
```

