<<<<<<< Updated upstream
---
title: "Lab 5"
author: "R4L"
date: "2/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(tidyverse)

milk <- read.csv('state_milk_production.csv')
head(milk)

milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)

milk1970 <- milk %>%
  filter(year == 1970)
```

## Team 
```{r}
team_milk <- milk %>%
  filter(state %in% c("Texas", "Colorado", "California", "Tennessee", "Illinois"))  

national <- milk %>%
  group_by(year) %>%
  summarise(milk = mean(milk_million))

team_milk$average <- national$milk

group_by(milk, year) %>%
  summarise(milk = mean(milk_million)) 
 
ggplot(data = team_milk, aes(x = year, y = milk_million, color =state))+
  geom_point()+
  geom_smooth(aes(x = year, y = average), se = FALSE)

arrange(team_milk, average) %>%
  top_n(1)

descteam_avg <- team_milk %>%
  mutate(avg = -average) %>%
  arrange(-average) 
top_n(descteam_avg,1)%>%
  select(region, state, year, milk_produced, milk_million, average)

```
## Individual

###Yen-Ting Shen
```{r}
milk1996 <- milk %>%
  filter(year == 1996)

ggplot(data= milk1996, aes(milk_million, fill = region), position = "fill")+
  geom_histogram(bins = 15)+
  ggtitle('Histogram of milk produced in 1996 by state')


```
```{r}
milk1996 %>%
  summarise(avg_milk_produced = mean(milk_million), median_milk_produced = median(milk_million))%>%
  arrange(desc(avg_milk_produced))
```
```{r}
arrange(milk1996, desc(milk_million))%>%
  top_n(1)
```
```{r}
descmilkyen <- milk1996 %>%
  mutate(milkrank = -milk_million) %>%
  arrange(-milk_million) 

top_n(descmilkyen,1)%>%
  select(region, state, year, milk_produced, milk_million)
  

```


###Emery Schattinger
```{r}
milk1998 <- milk %>%
  filter(year == 1998) 

ggplot(data = milk1998, aes(x = as.factor(year), y = milk_million, fill = region)) +
  geom_boxplot() + 
  ggtitle('Pounds of Milk Produced in 1998 by Region') + 
  scale_fill_discrete(name = 'Region') + 
  xlab('Year') +
  ylab('Milk Produced (Millions lb)')

```
```{r}
milk1998 %>%
  filter(year == 1998) %>%
  summarise(avg_milk_produced = mean(milk_million), 
            median_milk_produced = median(milk_million))%>%
  arrange(desc(avg_milk_produced)) 

```
```{r}
arrange(milk1998, desc(milk_million))%>%
  top_n(1)
```
```{r}
leastmilk <- milk1998 %>%
  mutate(milkrank = -milk_million) %>%
  arrange(-milk_million) 

top_n(leastmilk,1)%>%
  select(region, state, year, milk_produced, milk_million)
```

###Tiger Su
```{r}
milk1998<- milk%>%
  
  filter(year==1998)

```
```{r}
ggplot(data = milk1998)+
  
  geom_point(aes(x=state, y=milk_million,color=region))+
  
  theme(legend.position = "bottom")+
  
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5, vjust = 0.5))
  
  ggtitle('Milk Produced in 1998')
```
Average Milk Produced in 1998
```{r}
milk1998%>%
  
summarise(Average_Milk_Produced_1998=mean(milk_million))

```
Median of Milk Produced in 1998
```{r}
milk1998%>%
  
summarise(Median_of_Milk_Produced_1998=median(milk_million))

```
Most Milk Produced State in 1998
```{r}
milk1998%>%
  
arrange(desc(milk_million))%>%
  
  slice(1)
```
Lest Milk Produced State in 1998
```{r}
milk1998%>%
  
arrange(milk_million)%>%
  
  slice(1)
```


