---
title: "Lab6_R4L"
author: "R4L"
date: "2/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
COflights <- read_csv("https://files.osf.io/v1/resources/3z5as4pej8/providers/osfstorage/5a8ca28f57103100104584db")
```

## Team's Part

### Overall Questions 

1. 
2.
Why they are important, and the reasons why they are important
### Team's Plot

### Conclusion
(A “Conclusion” is similarly based on data, but could also be the logical consequence of a combination of findings. In this lab report, your conclusion should be the answer to your overall question.)
### Recommendation
why implementing it is important for the DIA managers
## Individual’s Part

### Yen-Ting Shen
```{r}


COflightsA <- COflights %>%
  filter(CANCELLATION_CODE == "A")
COflightsB <- COflights %>%
  filter(CANCELLATION_CODE == "B")
COflightsC <- COflights %>%
  filter(CANCELLATION_CODE == "C")
COflightsD <- COflights %>%
  filter(CANCELLATION_CODE == "D")
```

```{r}
filter(COflights, CANCELLED == 1) %>%
  count()
#Total number of flights that were cancelled in 2017 is 3656.

count(COflightsA)
# The total flighs were cancelled due to carrier issues  is 632.

632/3656
#The probability of cancelled flights due to carrier is 0.1728665.

count(COflightsB)
# The total flighs were cancelled due to weather is 2533.

2533/3656
#The probability of cancelled flights due to weather is 0.6928337.

count(COflightsC)
# The total flighs were cancelled due to National Air System is 487.

487/3656
#The probability of cancelled flights due to National Air System is 0.1332057.

count(COflightsD)
# The total flighs were cancelled due to security issues is 4.

4/3656
#The probability of cancelled flights due to security is 0.001094092.
```

```{r}
COflightsyen <- COflights %>%
  drop_na(CANCELLATION_CODE)

ggplot(COflightsyen, aes(x=CANCELLATION_CODE))+
  stat_count()+
  facet_wrap(.~MONTH)
```

```{r}
count(COflights, CARRIER) %>%
  arrange(n)
```

`

## Who did what?
(I want to know what each student did, in that student’s own words. Who did what and what non-defaults were used to generate which plots.)